Title here

### 2016-08-14 portfolio/text/ms.Rmd
Edit captions

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../figs/stan-gg-spoke2.pdf}
\caption{Adding permits reduces risk.
Two examples of expected revenue variability 
and median revenue for
owners of (A) individual halibut and (B) gillnet herring roe permits
(light blue)
compared with owners of the same permit plus one more (medium blue)
or two more permits (dark blue).
On the y-axis, dots and lines represent posterior median and 50\%
credible intervals.}
\label{fig:spokes}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability.pdf}
\caption{Fishing strategies with higher species diversity
have lower expected revenue variability.
On the y-axis, dots, thick lines, and thin lines represent posterior medians,
50\%, and 95\% credible intervals for
the `r nstr` most common strategies.
Thick black line, dark, and light grey shaded regions
indicate median, 50\%, and 95\% credible intervals
of strategy-level regression built into the heirarchical model.
}
\label{fig:across}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.1\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of generalizing and specializing from year to year for
individual permit holders across the `r nstr` most common strategies.}
\label{fig:within}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../figs/stan-gg-spoke2.pdf}
\caption{Diversifying permits reduces risk and usually increases revenue.
Two examples of expected revenue variability 
and median revenue for
owners of (A) individual halibut and (B) gillnet herring roe permits
(light blue)
compared with owners of the same permit plus one more (medium blue)
or two more permits (dark blue).
On the y-axis, dots and lines represent posterior median and 50\%
credible intervals.}
\label{fig:spokes}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability.pdf}
\caption{Individuals who choose
permits with higher species diversity
have lower expected revenue variability.
On the y-axis, dots, thick lines, and thin lines represent posterior medians,
50\%, and 95\% credible intervals for
the `r nstr` most common permit strategies.
Thick black line, and dark and light grey shaded regions
indicate median, 50\%, and 95\% credible intervals
of strastegy-level regression built into the heirarchical model.
}
\label{fig:across}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.1\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of (A) generalizing and (B) specializing from year to year for
individual permit holders across the `r nstr` most common strategies.
Changing species diversity from year to year 
is associated with higher variability
for individuals within the strategies above the zero line.
Generalizing (A) or specializing (B) is associated with
greater expected revenue to the right of the zero line
and lower expected revenue to the left of the zero line.
These effects are estimated holding
fishing season length constant from year to year.
}
\label{fig:within}
\end{center}
\end{figure}
